### 2023-09-14 main.tex
ghj

	\widehat{K}_{0}(x)=(1+x)\left(I+\frac{2x}{x+1}H^{''}_{right}\right)=\begin{pmatrix}

@@

	K_{0}=\left((2x+N)H^{''}_{left}+(x+N)I\right)\frac{(1+x)^{2}(2x+N)}{(x+1)^{2}(2x+N)}=\begin{pmatrix}

@@

		0&0&0&\ldots&0&1+x

@@

@@

	T^{\Delta}(x)=tr_{0}\left(K_{0}(x)U_{0}(x)\right)

@@

	\left[T^{\Delta}(x),T^{\Delta}(y)\right]=0\qquad \frac{\partial}{\partial x}\log (T^{\Delta}(0))=C_{1}H^{''}+C_{2}I

@@

The double row monodromy is given by

@@

We write $U_{0}(x)$ in the canonical basis of $V_{0}$ and we rename the elements, each of them acting on the quantum space $V$, has follows
\begin{comment}
	\begin{equation}
		U_{0}(x)=\begin{pmatrix}
			D_{11}(x)&B_{2}(x)&\ldots&B_{N}(x)\\
			C_{2}(x)&D_{22}(x)&\ldots&D_{2N}(x)\\
			\vdots&\vdots&\ddots&\vdots\\
			C_{N}(x)&D_{N2}(x)&\ldots&D_{NN}(x)
		\end{pmatrix}
	\end{equation}
\end{comment}
\begin{equation}
	U_{0}(x)=\begin{pmatrix}
		D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
		D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
		\vdots&\vdots&\ddots&\vdots&\vdots\\
		D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
		B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
	\end{pmatrix}
\end{equation}
The exchange relations for the elements of the above matrix can be found using \eqref{RURU}
\begin{itemize}
	\item for every $i\in\{1,\ldots,N-1\}$
	\begin{equation}\label{EX1}
		\begin{split}
			D_{N,N}(y)B_{i}(y)&=f(x,y)D_{N,N}(x)B_{i}(y)+f_{1}(x,y)B_{i}(x)D_{N,N}(y)\\&+f_{2}(x,y)\left(B_{i}(x)D_{i,i}(y)+\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}(x)D_{k,i}(y)\right)
		\end{split}	
	\end{equation}
	\begin{equation}\label{EX2}
		\begin{split}
			D_{i,i}(x)B_{i}(x)&=h(x,y)B_{i}(y)D_{i,i}(x)+h_{1}(x,y)B_{i}(x)D_{i,i}(y)\\&+h_{2}(x,y)B_{1}(x)D_{N,N}(y)+h_{3}(x,y)B_{i}(y)D_{N,N}(x)\\&+\frac{1}{2}h_{3}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}B_{k}(x)D_{k,i}(y)+h_{4}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}B_{k}(y)D_{k,i}(x)
		\end{split}
	\end{equation}
	\item  for every $i,j\in \{1,\ldots,N-1\}$ such that $i\neq j$
	\begin{equation}\label{EX3}
		\begin{split}
			D_{j,j}(x)B_{i}(y)&=B_{i}(x)D_{j,j}(y)+\frac{1}{2}h_{3}(x,y)\left(B_{i}(y)D_{i,i}(x)-B_{i}(x)D_{i,i}(y)\right)
			\\&+
			\frac{1}{2}h_{3}(x,y)\left(B_{i}(x)D_{N,N}(y)-B_{i}(y)D_{N,N}(x)\right)
			\\&+
			h_{1}(x,y)\left(B_{j}(x)D_{j,i}(y)-B_{j}(y)D_{i,j}(x)\right)
			\\&+
			\frac{1}{2}h_{3}(x,y)\sum_{k=1\,:\,k\neq i,j}\left(B_{k}(y)D_{k,i}(x)-B_{k}(x)D_{k,i}(y)\right)
		\end{split}
	\end{equation}

\end{itemize}
where
\begin{align}
	&f(x,y)=\frac{(x+y)(x-y-1)}{(x-y)(1+x+y)}&f_{1}(x,y)=\frac{(x+y)}{(x-y)(1+x+y)}\quad&f_{2}(x,y)=\frac{1}{(1+x+y)}\nonumber\\&h(x,y)=\frac{(1+x-y)(x+y+2)}{(x-y)(1+x+y)}
	&h_{1}(x,y)=-\frac{(x+y+2)}{(x-y)(1+x+y)}\quad&h_{2}(x,y)=\frac{(2+x-y)}{(x-y)(1+x+y)}\nonumber
	\\&h_{3}(x,y)=\frac{2}{(x-y)(1+x+y)}
\end{align}
\subsection{Charges}
The transfer matrix $T^{\Delta}(x)$ reads
\begin{equation}
	\begin{split}
		T^{\Delta}(x)=tr_{0}&\left(\begin{pmatrix}
			-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
			0&-x&0&\ldots&0&(N+2x)(\alpha_{2}-\beta_{2})\\
			\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
			0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
			0&0&0&\ldots&0&1+x
		\end{pmatrix}\right.
		\\& \left.
		\;\;\;\begin{pmatrix}
			D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
			D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
			\vdots&\vdots&\ddots&\vdots&\vdots\\
			D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
			B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
		\end{pmatrix}\right)\\
	=&
	(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)+\sum_{i=1}^{N-1}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
	\end{split}
\end{equation}
therefore, it is a polynomial in $x$ with exponents from $0$ to $2L+2$ 
\begin{equation}
	\begin{split}
		T^{\Delta}(x)=
		\sum_{k=0}^{2L+2}Q_{k}x^{k}
	\end{split}
\end{equation}
where, for all $k\in\{0,\ldots,2L+2\}$, we call these $Q_{k}$ the \textit{conserved charges} of the system. We also introduce 
\begin{equation}
	T_{0}(x)=(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)\quad\text{such that}\quad T_{\Delta}(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
\end{equation}
Arguing similarly we write the elements of $U_{0}(x)$ in a polynomial expansion as 
\begin{equation}
	D_{N,N}(x)=\sum_{a=0}^{2L+1}D_{N,N}^{a}x^{a}\quad D_{ii}(x)=\sum_{a=0}^{2L+1}D_{ii}^{a}x^{a}\quad B_{i}(x)=\sum_{a=0}^{2L-1}B_{i}^{a}x^{a}\quad D_{i,j}(x)=\sum_{a=0}^{2L}D_{i,j}^{a}x^{a}
\end{equation}
 Only the first three coefficients of the diagonal elements and the first coefficient of the non diagonal elements do survive when $x\to \infty$, therefore we only compute them. We obtain:
\begin{itemize}
	\item For $D_{N,N}(x)$:

@@

Consider the matrix $Q_{0}^{2L}$ defined in \eqref{Q0Exp}. All terms are diagonal except the last one. However, this last non-diagonal term acts diagonally on the states. Indeed, can be identified with the second Casimir of the $gl(N-1)$ subalgebra. We denote it by $\hat{C}_{2}^{N-1}$ and it reads

@@

We denote its eigenvector by $C_{2}^{N-1}$. On the Bethe states (and on the decomposition into irreducible representation of the spin chain) it acts diagonally with eigenvalues $C_{2}^{N-1}$ given in terms of shifted weights, i.e. 

@@

with $\mu_{j}$ the representation labels of tensor product over the chain of the fundamental representation of $gl(N)$ (it can be decomposed by branching rule).  
Thus the eigenvalues of the transfer matrix can be writen as 

@@

@@

While, for $i,j\in\{1,\ldots,N-1\}$ such that $i\neq j$

@@

\left[D_{j,j}^{2L},B_{i}^{2L-1}\right]=0\qquad \left[B_{i}^{2L-1},B_{j}^{2L-1}\right]=0\qquad \left[B_{i}^{2L-1},D_{j,i}^{2L}\right]=0%\qquad \left[D_{12}^{2L},B_{2}^{2L-1}\right]=0\qquad \left[D_{11}^{2L},B_{2}^{2L-1}\right]=0

@@

Since $Q^{2L}$ and $H^{''}$ are isospectral the above matrix $W$ still maps the non-equilibrium eigenvectors onto the equilibrium ones. The advantage is that now we can do more with the above expression. Firstly the eigenvalues $\Lambda_{\bm{m}}$ can be explicitly computed and secondly, using exchange relation between charges, we rewrite \eqref{WInCharges} in a better form that can be used to extract the steady state by rising the vacuum state. We first show the procedure in the $gl(2)$ case, and then we generalize it to arbitrary number of species $N$. 

@@

In the case of $gl(2)$ we have that for every magnon number $m\in\{0,\ldots,L\}$ non-equilibrium eigenvectors $|\Psi_{m}\rangle$ of $H^{''}$, are written in terms of the eigenvectors $|\Psi_{m}^{0}\rangle$ of the equilibrium Hamiltonian $H_{0}$ by the following formula 

@@

In this simpler situation the double row monodromy reads

@@

Power expanding the matrix $W$ with respect to $\Delta=(\alpha-\beta)$ we obtain 

@@

		&=(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left(Q_{0}^{2L}-2j(D_{2,2}^{2L}+D_{1,1}^{2L})+4j(j-1)N\right)\\

>>>>

	\widehat{K}_{a}(x)=(1+x)\left(I+\frac{2x}{x+1}H^{''}_{right}\right)=\begin{pmatrix}

@@

	K_{a}(x)=\frac{\left((2x+N)H^{''}_{left}+(x+N)I\right)}{(x+1)^{2}(2x+N)}=\begin{pmatrix}

@@

		0&0&0&\ldots&0&N+x

@@

where the lower index $a$ means that they are written in the canonical basis of the space $V_{a}=\mathbb{C}^{N}$, for $a\in\{0,\ldots,L\}$ and where $x,y\in\mathbb{C}$ are called spectral parameters.  

@@

	T(x)=tr_{0}\left(K_{0}(x)U_{0}(x)\right)

@@

	\left[T(x),T(y)\right]=0\qquad \frac{\partial}{\partial x}\log (T(x))\lvert_{x=0}=C_{1}H^{''}+C_{2}I

@@

The double row monodromy $U_{0}(x)$ is given by

@@

We write $U_{0}(x)$ in the canonical basis of $V_{0}$ and we rename its elements, each of them acting on the quantum space $V$, has follows
\begin{comment}
	\begin{equation}
		U_{0}(x)=\begin{pmatrix}
			D_{11}(x)&B_{2}(x)&\ldots&B_{N}(x)\\
			C_{2}(x)&D_{22}(x)&\ldots&D_{2N}(x)\\
			\vdots&\vdots&\ddots&\vdots\\
			C_{N}(x)&D_{N2}(x)&\ldots&D_{NN}(x)
		\end{pmatrix}
	\end{equation}
\end{comment}
\begin{equation}
	U_{0}(x)=\begin{pmatrix}
		D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
		D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
		\vdots&\vdots&\ddots&\vdots&\vdots\\
		D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
		B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
	\end{pmatrix}
\end{equation}
The exchange relations for the elements of the above matrix can be found using \eqref{RURU} and they read:
\begin{itemize}
	\item for every $i\in\{1,\ldots,N-1\}$
	\begin{equation}\label{EX1}
		\begin{split}
			D_{N,N}(y)B_{i}(y)&=f(x,y)D_{N,N}(x)B_{i}(y)+f_{1}(x,y)B_{i}(x)D_{N,N}(y)\\&+f_{2}(x,y)\left(B_{i}(x)D_{i,i}(y)+\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}(x)D_{k,i}(y)\right)
		\end{split}	
	\end{equation}
	\begin{equation}\label{EX2}
		\begin{split}
			D_{i,i}(x)B_{i}(x)&=h(x,y)B_{i}(y)D_{i,i}(x)+h_{1}(x,y)B_{i}(x)D_{i,i}(y)\\&+h_{2}(x,y)B_{1}(x)D_{N,N}(y)+h_{3}(x,y)B_{i}(y)D_{N,N}(x)\\&+\frac{1}{2}h_{3}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}B_{k}(x)D_{k,i}(y)+h_{4}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}B_{k}(y)D_{k,i}(x)
		\end{split}
	\end{equation}
	\item  for every $i,j\in \{1,\ldots,N-1\}$ such that $i\neq j$
	\begin{equation}\label{EX3}
		\begin{split}
			D_{j,j}(x)B_{i}(y)&=B_{i}(x)D_{j,j}(y)+\frac{1}{2}h_{3}(x,y)\left(B_{i}(y)D_{i,i}(x)-B_{i}(x)D_{i,i}(y)\right)
			\\&+
			\frac{1}{2}h_{3}(x,y)\left(B_{i}(x)D_{N,N}(y)-B_{i}(y)D_{N,N}(x)\right)
			\\&+
			h_{1}(x,y)\left(B_{j}(x)D_{j,i}(y)-B_{j}(y)D_{i,j}(x)\right)
			\\&+
			\frac{1}{2}h_{3}(x,y)\sum_{k=1\,:\,k\neq i,j}\left(B_{k}(y)D_{k,i}(x)-B_{k}(x)D_{k,i}(y)\right)
		\end{split}
	\end{equation}

\end{itemize}
where
\begin{align}
	&f(x,y)=\frac{(x+y)(x-y-1)}{(x-y)(1+x+y)}&f_{1}(x,y)=\frac{(x+y)}{(x-y)(1+x+y)}\quad&f_{2}(x,y)=\frac{1}{(1+x+y)}\nonumber\\&h(x,y)=\frac{(1+x-y)(x+y+2)}{(x-y)(1+x+y)}
	&h_{1}(x,y)=-\frac{(x+y+2)}{(x-y)(1+x+y)}\quad&h_{2}(x,y)=\frac{(2+x-y)}{(x-y)(1+x+y)}\nonumber
	\\&h_{3}(x,y)=\frac{2}{(x-y)(1+x+y)}
\end{align}
\subsection{Charges}
The transfer matrix $T^{\Delta}(x)$ reads
\begin{equation}
	\begin{split}
		T^{\Delta}(x)=%tr_{0}&\left(\begin{pmatrix}
			%-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
		%	0&-x&0&\ldots&0&(N+2x)(\alpha_{2}-\beta_{2})\\
		%	\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
		%	0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
		%	0&0&0&\ldots&0&N+x
	%	\end{pmatrix}\right.
	%	\;\;\;\begin{pmatrix}
	%		D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
	%		D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
	%		\vdots&\vdots&\ddots&\vdots&\vdots\\
	%		D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
	%		B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
	%	\end{pmatrix}\right)\\
	%=&
	(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)+\sum_{i=1}^{N-1}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
	\end{split}
\end{equation}
By construction,$T(x)$ is a polynomial in $x$ with exponents from $0$ to $2L+2$ 
\begin{equation}
	\begin{split}
		T(x)=
		\sum_{k=0}^{2L+2}Q_{k}x^{k}
	\end{split}
\end{equation}
where, for all $k\in\{0,\ldots,2L+2\}$, we call $Q_{k}$ the \textit{conserved charges} of the system. We also introduce 
\begin{equation}
	T_{0}(x)=(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)\quad\text{such that}\quad T(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
\end{equation}
Arguing similarly we write the elements of $U_{0}(x)$ in a polynomial expansion as 
\begin{equation}
	D_{N,N}(x)=\sum_{a=0}^{2L+1}D_{N,N}^{a}x^{a}\quad D_{ii}(x)=\sum_{a=0}^{2L+1}D_{ii}^{a}x^{a}\quad B_{i}(x)=\sum_{a=0}^{2L-1}B_{i}^{a}x^{a}\quad D_{i,j}(x)=\sum_{a=0}^{2L}D_{i,j}^{a}x^{a}
\end{equation}
 In the following we will study the charge expansion of $T^{\Delta}(x)$ when $x\to \infty$. As it will be clear in the following, only the first three coefficients for the diagonal elements and only the first one for the non-diagonal elements will be needed. Therefore, using \eqref{RURU}, we compute: 
\begin{itemize}
	\item For $D_{N,N}(x)$:

@@

Consider the matrix $Q_{0}^{2L}$ defined in \eqref{Q0Exp}. All terms are diagonal except the last one. This last non-diagonal can be identified with the second Casimir of the $gl(N-1)$ subalgebra. We denote it by $\hat{C}_{2}^{N-1}$ and it reads

@@

We denote its eigenvector by $C_{2}^{N-1}$. Since the configuration space of the process is given by the tensor product of the first fundamental representation of $gl(N)$, we can decompose it in a direct sum of irreducible representation of $gl(N)$. The Bethe states belong to the configurations space, and thus we can write them as a direct sum of vectors, each belonging to an irreducible representation of $gl(N)$. On these irreducible vectors . $\hat{C}_{2}^{N-1}$ acts diagonally with eigenvalues $C_{2}^{N-1}$ given in terms of shifted weights, i.e. 

@@

with $\mu_{j}$ the representation labels of irreducible representation of $gl(N)$. This argument allows to write explicit expression for the eigenvalues of $Q_{0}^{2L}$, indeed 

@@

\end{equation} }

@@

While, for $i,j,k\in\{1,\ldots,N-1\}$ such that $i\neq j$, $k\neq i,h$

@@

\left[D_{j,j}^{2L},B_{i}^{2L-1}\right]=0\qquad \left[B_{i}^{2L-1},B_{j}^{2L-1}\right]=0\qquad \left[B_{i}^{2L-1},D_{j,i}^{2L}\right]=0\qquad \left[B_{k}^{2L-1},D_{j,i}^{2L}\right]=0%\left[D_{12}^{2L},B_{2}^{2L-1}\right]=0\qquad \left[D_{11}^{2L},B_{2}^{2L-1}\right]=0

@@

Since $Q^{2L}$ and $H^{''}$ commutes the above matrix $W$ still maps the non-equilibrium eigenvectors onto the equilibrium ones. The advantage is that now we can do more with the above expression. Firstly the eigenvalues $\Lambda_{\bm{m}}$ can be explicitly computed and secondly, using exchange relation between charges, we rewrite \eqref{WInCharges} in a better form that can be used to extract the steady state by rising the vacuum state. We first show the procedure in the $gl(2)$ case, and then we generalize it to arbitrary number of species $N$. 

@@

Here, the multi-species stirring process reduces to the Simple Symmetric Exclusion Process (SSEP). We have that for every magnon number $m\in\{0,\ldots,L\}$ non-equilibrium eigenvectors $|\Psi_{m}\rangle$ of $H^{''}$, are written in terms of the eigenvectors $|\Psi_{m}^{0}\rangle$ of the equilibrium Hamiltonian $H_{0}$ by the following formula 

@@

The double row monodromy reads

@@

Power expanding the matrix $W$ with respect to $\Delta_{i}=(\alpha_{i}-\beta_{i})$ for all $i\in\{1,\ldots,N-1\}$ we obtain 

@@

		&=(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left(Q_{0}^{2L}-2j(D_{2,2}^{2L}+D_{1,1}^{2L})+4j(j-1)\right)\\
